First look at Spacetime

### 2019-10-30 Output/error_reduction_analysis.tex
done

\section*{Convergence rate}
The code right now seems to solve the problem, as can be seen by Figure~\ref{fig:time-slice}:
Increasing $L$ (thereby increasing $\dim X_\delta$, yields an error reduction.
We discern a pre-asymptotic regime: the error hardly decreases between levels $L=1$
and $2$. Moreover, errors seem to taper off near the final levels $L$, which may
have something to do with our solver tolerance.

@@

\section*{Computational cost}
Let's measure the time it takes to perform a single application of the system
matrix. We do not take into account the setup cost (like
computing $\Sigma$ and $\Theta$). Figure~\ref{fig:linearity} paints a slightly
demotivating picture, in that the bottom graph is not constant. We do have to
place an asterisk here: for small systems, the produced numbers are averaged over
a small number of iterations, so they change a lot from run to run.
\begin{figure}[h!]
  \includegraphics[width=0.6\linewidth]{error_reduction_linearity.pdf}
  \caption{Top: time (s) per apply; bottom: time (ms) per apply per DoF.}
  \label{fig:linearity}
\end{figure}

>>>>

\section*{Convergence rate}
The code right now seems to solve the problem, as can be seen by Figure~\ref{fig:time-slice}:
Increasing $L$ (thereby increasing $\dim X_\delta$, yields an error reduction.
We discern a pre-asymptotic regime: the error hardly decreases between levels $L=1$
and $2$. Moreover, errors seem to stagnate/ near the final levels $L$, which may
have something to do with our solver tolerance.

@@

\section*{Computational cost}
Let's measure the time it takes to perform a single application of the system
matrix. We do not take into account the setup cost (like computing $\Sigma$ and
$\Theta$). Figure~\ref{fig:linearity} reveals a modest increase in the time spent
per apply per doublenode, which hints at a very slight superlinearity in the
computational cost of a single apply. However, we see only a factor-2 increase
over the course of the simulation.
\begin{figure}[h!]
  \includegraphics[width=0.6\linewidth]{error_reduction_linearity.pdf}
  \caption{Top: time (s) per apply; bottom: time (ms) per apply per DoF.}
  \label{fig:linearity}
\end{figure}
